---
format:
  pdf:
    documentclass: report
    papersize: letter
    fontsize: 12pt
    mainfont: Times New Roman
    geometry:
      - left=1.5in
      - right=1in
      - top=1in
      - bottom=1in
    include-before-body:
      - frontmatter/information.tex
      - frontmatter/title-page.tex
      - frontmatter/copyright-page.tex
      - frontmatter/committee-page.tex
      - frontmatter/abstract.tex
      - frontmatter/acknowledgments.tex
      - frontmatter/table-of-contents.tex
    number-sections: true
    citation-style: apa
    bibliography: bibliography/example-bibliography.bib
    csl: bibliography/apa-6th-edition.csl
    include-in-header: frontmatter/formating.tex
---

```{r}
#| lablel: set-up
#| include: false # Use to hide code and resutls

# I recommend having a hidden code chunk to prep any packages or data sets!

library(tidyverse)
library(kableExtra)

data("starwars")
```

# Literature Review

There will probably be lots of citations here for many articles or even software like R [@r_core_team_r_2024].

# Analysis

## How to Add Figures

```{r}
#| label: example-figure
#| echo: false # Use to hide code but not results
#| fig-cap: "Example Figure Title/Caption"

starwars |>
  filter(!is.na(height), !is.na(mass), !is.na(species)) |>
  filter(species %in% (starwars |> count(species, sort = TRUE) |> slice_head(n = 2) |> pull(species))) |>
  ggplot(aes(x = height, y = mass, color = species)) +
  geom_point() +
  labs(
    title = "Height v. Mass for most Common Starwars Species", 
    x = "Height",
    y = "Mass",
    color = "Species") +
  theme_bw()
```

## How to Add Tables

```{r}
#| label: example-table
#| echo: false # Use to hide code but not results
#| tbl-cap: "Example Table Title/Caption"

starwars |>
  head(c(3, 3)) |>
  kable()
```

# Conclusion

Write something here I guess.

## Computational Details

The results in this paper were obtained using `R` 4.4.1. `R` itself and all 
packages used are available from the Comprehensive `R` Archive Network (CRAN) at 
https://CRAN.R-project.org/.

# REFERENCES {.unnumbered}

::: {#refs}
:::

\appendix

<!-- Store original definitions formatting -->
\let\oldclearpage\clearpage
\let\oldcleardoublepage\cleardoublepage

<!-- Disable page breaks -->
\let\clearpage\relax
\let\cleardoublepage\relax

# Super Cool Fancy Function

<!-- Restore original formatting -->
\let\clearpage\oldclearpage
\let\cleardoublepage\oldcleardoublepage

```{r}
# Add your fancy function here!
```

# Slightly Less Cool Fancy Something

```{r}
# Got more fancy functions, or figures, or tables, 
# or pretty much anything?
```